---
title: "p8105_hw1_lc3391"
author: "Lu Chen"
date: "09/17/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

#Problem 1

##Creating a data frame
```{r problem1_parta}
library(tidyverse)

la_df= tibble(
  norm_samp = rnorm(8),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("a","b","c","d","e","f","g","h"),
  vec_factor = factor(c("low","med","high","low","low","med","high","high"))

)

mean(pull(la_df, norm_samp))
mean(pull(la_df, norm_samp_pos))
mean(pull(la_df, vec_char))
mean(pull(la_df, vec_factor))

```

- The mean of the numeric vector, norm_samp, is `r mean(pull(la_df, norm_samp))`;
- The mean of the logical vector, norm_samp_pos is `r mean(pull(la_df, norm_samp_pos))`;
- And NO mean could be taken for the character vector and factor vector.

##converting variables from one type to another
```{r problem1_partb, warning = FALSE}

#convert the logical vector to numeric and multiply the random sample by the result
as.numeric(pull(la_df, norm_samp_pos))*pull(la_df, norm_samp)

#convert the logical vector to factor and multiply the random sample by the result
as.factor(pull(la_df, norm_samp_pos))*pull(la_df, norm_samp)

#convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
as.numeric(as.factor(pull(la_df, norm_samp_pos)))*pull(la_df, norm_samp)
```


#Problem 2
```{r problem2_part1}
p2_df= tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_log2 = x + y > 1,
  vec_num2 = as.numeric(vec_log2),
  vec_fac2 = as.factor(vec_log2)
)

```

##Short descprition
- the number of row in `p2_df` is `r nrow(p2_df)`;
- the number of column in `p2_df` is `r ncol(p2_df)`;
- the mean of the x is `r mean(pull(p2_df, x))`;
- the mean of the y is `r mean(pull(p2_df, y))`;
- the median of the x is `r median(pull(p2_df, x))`;
- the median of the y is `r median(pull(p2_df, y))`;
- the standard deviation of x is `r sd(pull(p2_df, x))`;
- the proportion of cases for which x + y > 1 is `r mean(pull(p2_df, vec_log2))`;

##Scatterplot
```{r problem2_part2}
#A scatterplot for logical vector
ggplot(p2_df, aes (x = x, y = y, color = vec_log2)) + geom_point()

#A scatterplot for numeric vector
ggplot(p2_df, aes (x = x, y = y, color = vec_num2)) + geom_point()

#A scatterplot for factor vector
ggplot(p2_df, aes (x = x, y = y, color = vec_fac2)) + geom_point()

```

##Comments on color scale
- The first and third scatterplot have two color in the scale: one represnts TRUE and the other represents FALSE.
- The second scatterplot uses a blue color bar to represent different scale. Smaller values associate with darker blue while bigger numbers associate with lighter blue.

```{r problem2_part3}
ggsave("Problem2_firstplot.pdf",plot = ggplot(p2_df, aes (x = x, y = y, color = vec_log2)) + geom_point())

```

